%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
\newcommand{\quotes}[1]{``#1''}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer} % Job title
  {Grisú} % Organization
  {Self-employed, Colombia} % Location
  {Jul. 2023 - Present (Oct. 2023)} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Played a pivotal role in enhancing the performance and functionality of a \textbf{React Native} \textbf{TypeScript} application, driving improvements in code quality and user satisfaction for Industrias Falcon.}
      \item {Designed and implemented a Workshop inventory management system in \textbf{React}, streamlining operations for Industrias Falcon, and showcasing my expertise in building practical solutions.}
      \item {Successfully deployed two web applications (one in \textbf{React} and the other in Angular) to \textbf{AWS Amplify}, ensuring seamless and scalable user experiences for Industrias Falcon.}
      \item {Led the auditing and development for 'EcoDrive', leveraging \textbf{React Native}, \textbf{Kafka}, \textbf{Redis}, and \textbf{Python Fast API}, accelerating a 4-month project timeline into mere weeks.}
      \item {Crafted and launched a nostalgia-driven \textbf{React Native} App, the Yak Bak 90's toy simulator.}
      \item {Provided architectural design consultancy for Industrias Falcon Colombia.}
      \item {Conceptualized and rolled out a robust architecture for GameConnect.}
      \item {Offered the services of \textbf{UI Design} to GameConnect, paving the way for seamless code implementation.}
      \item {Engineered and revitalized the company's landing page using \textbf{React}, leading to a surge in site traffic by 150\%.}
      \item {Actively driving the development of an engaging Hyper-Casual game using \textbf{React Native} and \textbf{Godot}.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Full Stack Developer} % Job title
  {ArcDesign} % Organization
  {Part-time, Spain} % Location
  {Jul. 2023 - Present (Oct. 2023)} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Innovated an advanced algorithm using hashmaps, MQTT (using \textbf{EMQX}) and geohashes, enhancing the application's performance by 70\%.}
      \item {Integrated the algorithm in a \textbf{React Native} environment, improving mobile app performance. (https://hiwayapp.io)}
      \item {Led the deployment of several static websites on \textbf{AWS} and Hostinger using \textbf{React}. (https://arcdesign.io)}
    \end{cvitems}
  }
  %---------------------------------------------------------
  \cventry
  {Problem Solver} % Job title
  {Design Systems Inno} % Organization
  {Contract, Colombia} % Location
  {Jan. 2023 - Jun. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Architected a system for internal APIs, using \textbf{RabbitMQ} for asynchronous task management. Clients receive ID tickets for tracking while the backend efficiently handles web scraping and parsing, ensuring timely user feedback.}
      \item {Developed internal APIs to automate some internal processes using \textbf{Go Fiber}, \textbf{Python Fast API}, and \textbf{MongoDB}.}
      \item {Created web scraping tools and custom HTML parsers in \textbf{Python} using \textbf{Playwright} and \textbf{Beautiful Soup}.}
      \item {Paired with partners to fix critical bugs, ensuring on-time software deliveries and maintaining high quality.}
      \item {Developed an automation script in Python for efficient contract signing.}
      \item {Developed various administration panels using \textbf{React (Redux + Saga)}.}
      \item {Optimized project builds for some \textbf{React} web applications, reducing build sizes from 3.46 MB to around 886 KB and in some others even a little bit more.}
      \item {I Assisted in improving the quality and speed of \textbf{Dockerfiles} for \textbf{React} and \textbf{Angular} web applications.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Security Consultant} % Job title
  {Design Systems Inno} % Organization
  {Contract, Colombia} % Location
  {Dec. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed an external penetration testing engagement for a week and a half.}
      \item {Documented the findings in the software and part of the infrastructure.}
      \item {Documented some advices to improve the software and infrastructure quality}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Red Teamer} % Job title
  {Aligo Defensores Informáticos} % Organization
  {In person, Colombia} % Location
  {Aug. 2022 - Oct. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Pentesting websites.}
      \item {Pentesting tooling development (\textbf{Go} and \textbf{Nim}).}
      \item {Phishing campaigns developed.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Cyber Security Analyst} % Job title
  {GETA Club Play} % Organization
  {Remote, Colombia} % Location
  {Oct. 2021 - Jun. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {I used the DAST capabilities of \textbf{OWASP ZAP} to automatically review the company's web
                  applications.}
      \item {I used \textbf{SonarQube}'s SAST capabilities to automatically review the company's code.}
      \item {I developed an "economic" DevSecOps pipeline to avoid possible common
                  vulnerabilities.}
      \item {I worked closely with the AI team to sanitize requests made by users and avoid \textbf{SQL injections}.}
      \item {With some limited resources I Worked closely with IT to implement a good password
                  policy (KeePass).}
      \item {I Worked closely with IT to implement backup policies for employee files and
                  repositories.}
      \item {I was given an external pentesting report with about 800 vulnerabilities in our
                  projects, and I reduced that number to less than 390 (i.e. fixed about 50\% of
                  vulnerabilities) in a span of 4 months.}
      \item {I simulated and implemented reverse engineering attacks on some project APKs in order
                  to address, together with the development team, a possible way to mitigate the possibility
                  of a Hacker obtaining useful or critical information about our core business.}
      \item {Together with the IT team, I developed a Security Plan based on the \textbf{ISO/27001}
                  standard.}
      \item {I implemented hardening for some of our infrastructure processes.}
      \item {I worked alongside the IA team to develop a part of the SOC (Security Operations
                  Center) that can deliver value to our technical and non-technical employees.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Cyber Security Trainee} % Job title
  {GETA Club Play} % Organization
  {Remote, Colombia} % Location
  {Aug. 2021 - Sep. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {I did a Cyber security planning for 4 months to 3 company's products.}
      \item {I found and reported common OWASP based vulnerabilities.}
      \item {I worked along with the development team to fix the vulnerabilities found.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Quality Assurance Tester} % Job title
  {GETA Club Play} % Organization
  {Remote, Colombia} % Location
  {Feb. 2021 - Aug. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {I captured 100+ bugs within the span of 4 months while conducting quality assurance
                  testing on 7 company products thereby increasing the acceptance criteria of the top-rung
                  corporate “chiefs”.}
      \item {I document and record analyzed bugs for quality assurance every week.}
      \item {I performed more than 15\% testing through automation and remaining testing manually
                  using Selenium.}
      \item {I refactored and retrofitted legacy a \textbf{C++ WebAssembly} application, improving code
                  quality by 45\%.}
      \item {I completed more than 20 "Desk Checks" to reduce on 25\% the amount of Pull Request
                  and therefore save the Tech Lead's time.}
      \item {I helped to document 2 \textbf{Unity 3D} projects and also checked a documentation of an
                  \textbf{Angular/.Net Core} project.}
      \item {I did functional, online, manual, usability and stress tests.}
    \end{cvitems}
  }
  %---------------------------------------------------------
\end{cventries}
