%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activities}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %---------------------------------------------------------
  \cventry
  {Participant} % Affiliation/role
  {CivicaPay Hackathon 2022} % Organization/group
  {Medellín} % Location
  {Mar. 2022 - Mar. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {\textbf{First place} achieved among more than 52 teams and 16 universities in
                  Medellín in the Hackathon CivicaPay of 2022.}
      \item {The solution was made with \textbf{Flutter}, \textbf{Python 3} and \textbf{Docker}.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Youngermaster - Hacker} % Affiliation/role
  {HackTheBox} % Organization/group
  {Worldwide} % Location
  {Dec. 2021 - Dec. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {\href{https://app.hackthebox.com/profile/643960}{3rd place in Colombia's HackTheBox Ranking. (Click to View)}}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Chrome Web Store} % Affiliation/role
  {Developer} % Organization/group
  {Worldwide} % Location
  {Jan. 2022 - Jan. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {\href{https://chrome.google.com/webstore/detail/youtube-short-redirector/mnijpcchboaebolejillacjcmngnhppg}
                  {I pusblished an extension to redirect YouTube shorts to a video view. (Click to View)}}
      \item {\href{https://chrome.google.com/webstore/detail/platzi-community-wrapper/dakgbbfpefoofghfbkopnbnpadeblbep}
                  {I pusblished an extension to remove the Platzi's academy comments. (Click to View)}}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Google Play Store} % Affiliation/role
  {Mobile developer} % Organization/group
  {Worldwide} % Location
  {Nov. 2019 - Apr. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {\href{https://play.google.com/store/apps/details?id=com.grisu.accelerometer}{
                    \textbf{Accelerometer} - An app with more than 100 downloads using Flutter to obtain the data from your accelerometer
                    in a time 'x', with time intervals 'y' in milliseconds and send the information wherever you
                    want (Email, WhatsApp, etc.), and store that information in a txt file on your phone to be
                    used in another scenarios. (Click to View)}}
      \item {\href{https://play.google.com/store/apps/details?id=com.grisu.anthropometric_evaluator}{
                    \textbf{Anthropometric Evaluator} - An application using Flutter that provides information
                    and evaluates some of the parts of your body with certain measurements to provide a more
                    complete analysis than the common BMI, for people who go to the gym. (Click to View)}}
    \end{cvitems}
  }
\end{cventries}
